Streaming CityJSON datasets

### 2024-05-02 paper/main.tex
introductions

However, the version 1.0 of CityJSON had one limitation: its structure for storing the coordinates of the geometries (see Figure~\ref{fig:cj_idea}) made the \emph{streaming} of very large datasets complex, if not impossible.
As further defined in Section~\ref{sec:streaming}, streaming refers to the possibility of downloading/transferring/processing a dataset without having to load it all in memory.
Since datasets of 3D cities are nowadays very large (it is not uncommon to have CityGML-XML files over 2GB), the processing CityJSON files is in practice an issue.

@@

We present in this paper \emph{CityJSON Text Sequences} (\emph{CityJSONSeq} in short in the following), a format based on \emph{JSON Text Sequences}~\citep{IETF-JSONSeq} and CityJSON, and inspired by \emph{GeoJSON Text Sequences}~\citep{IETF-GeoJSONSeq}. 
CityJSONSeq was added to the CityJSON version 2.0 standard that was released in 2023 (and also standardised by the OGC, see \citet{OGC-CityJSON-v20}).
As further described in Section~\ref{sec:cityjsonseq}, the idea is to decompose a (often large) CityJSON file into its individual \emph{features} (\eg\ each \texttt{Building}, each \texttt{Bridge}, etc.) and create several JSON objects of a newly defined type \texttt{CityJSONFeature}.
These objects are either serialised into a text file, or streamed from a server to client or from one application to another.
This allows us to avoid a large list of vertices that need to be indexed, as it is the case with CityJSON files (see Section~\ref{sec:cityjson} for details).
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/cj_idea}
  \caption{An example of a CityJSON file. The vertices are stored in a global list, and the position of the vertices in that list are used to represent the boundaries of the geometries (represented by the arrows, many have been left out for clarity).}%
\label{fig:cj_idea}
\end{figure}

>>>>

However, the version 1.0 of CityJSON had one limitation: its structure for storing the coordinates of the geometries (see Figure~\ref{fig:cj_idea}) made the \emph{streaming} of very large datasets complex, if not impossible.
As further defined in Section~\ref{sec:streaming}, streaming refers to the possibility of downloading/transferring/processing a dataset without having to load it all in memory.
Given the increasing size of datasets of 3D cities, with CityGML-XML files often exceeding 2GB, the processing of CityJSON files has become a practical challenge.

@@

We present in this paper \emph{CityJSON Text Sequences} (henceforth referred to as \emph{CityJSONSeq}), a format based on \emph{JSON Text Sequences}~\citep{IETF-JSONSeq} and CityJSON, and inspired by \emph{GeoJSON Text Sequences}~\citep{IETF-GeoJSONSeq}. 
CityJSONSeq was added to the CityJSON version 2.0 standard that was released in 2023 (and also standardised by the OGC, see \citet{OGC-CityJSON-v20}).
As further described in Section~\ref{sec:cityjsonseq}, the idea is to decompose a (often large) CityJSON file into its individual \emph{features} (\eg\ each \texttt{Building}, each \texttt{Bridge}, etc.) and create several JSON objects of a newly defined type \texttt{CityJSONFeature}.
These objects are either serialised into a text file, or streamed from a server to client or from one application to another.
This allows us to avoid a large list of vertices that need to be indexed, as it is the case with CityJSON files (see Section~\ref{sec:cityjson} for details).
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/cj_idea}
  \caption{An example of a CityJSON file. The vertices are stored in a global list, and the position of the vertices in that list are used to represent the boundaries of the geometries (represented by the arrows, many have been left out for clarity).}%
\label{fig:cj_idea}
\end{figure}
